### 2024-05-07 thesis/chapters/05-evaluation.tex
Complete evaluation

\section{MaFaulDa in k-nearest neighbors}
The four outlined experiments involve testing sets of features with very few members to see the effects in predictions when reducing the information content about machine status to the minimum. First, the attributes are left in the complete count after extraction. Then, all of their combinations are enumerated, and the resulting accuracy distribution is matched against accuracy after feature selection with similarity metrics.

@@

Labeling every \nth{10} samples (to 10\% of the dataset) with a tumbling window of 10 samples reduces maximum accuracy for the three-predictor model compared to data points without gaps in labels. Time-domain features it is decreased by 9.9\% to 66.78\%, and by 14.93\% for frequency-domain features to 67.00\% (Fig.~\ref{fig:evaluation:label-skips-online}). More annotations can be scrapped in the case of a relabeled dataset where keeping just 0.02\% of the class labels produces a decrease by 13.7\% to 68.79\% for time domain attributes, and by 16.59\% to 66.25\% for frequency domain attributes.

%TODO
\section{Industrial dataset analysis}

\subsection{Data logger validation}

\begin{figure}[h]
    \centering
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{assets/results/standing-fan/waveform.png}
        \caption{Time waveform}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{assets/results/standing-fan/standing-fan-accel.png}
        \caption{Estimation of rotation speed}
    \end{subfigure}
    \caption{Vibrations from the back of a standing fan in radial direction}
\end{figure}

\subsection{Feature ranges}
% Amplitude histograms - 20m/s^2, 40m/s^2, 150m/s^
% Histograms of machinery measurements

% Box plots of features
\begin{figure}[h]
    \centering
    \begin{subfigure}[b]{\textwidth}
        \includegraphics[width=\textwidth]{assets/results/feature-values/pumps-TD-dim-3.png}
        \caption{Time-domain features}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{\textwidth}
        \includegraphics[width=\textwidth]{assets/results/feature-values/pumps-FD-dim-3.png}
        \caption{Frequency-domain features}
    \end{subfigure}
    \caption{Feature range in pumps}
\end{figure}

\subsection{Time-frequency waveforms}
\begin{figure}[h]
    \centering
    \begin{subfigure}[b]{0.32\textwidth}
        \includegraphics[width=\textwidth]{assets/results/eda/frequency-spectrum-motors.png}
        \caption{Motors}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.32\textwidth}
        \includegraphics[width=\textwidth]{assets/results/eda/frequency-spectrum-pumps.png}
        \caption{Pumps}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.32\textwidth}
        \includegraphics[width=\textwidth]{assets/results/eda/frequency-spectrum-compressors.png}
        \caption{Compressor}
    \end{subfigure} 
    \caption{Frequency domain}
\end{figure}

% Time-frequency spectrum

% Low frequencies (under 1KHz)

\begin{figure}[h]
    \centering
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/time-frequency-spectrum/K3-z-STFT-1kHz.png}
        \caption{K3}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/time-frequency-spectrum/M1-2-z-STFT-1kHz.png}
        \caption{M1-2}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/time-frequency-spectrum/P1-3-z-STFT-1kHz.png}
        \caption{P1-3}
    \end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/time-frequency-spectrum/P3-3-z-STFT-1kHz.png}
        \caption{P3-3}
    \end{subfigure}
    \caption{Time frequency spectrum}
\end{figure}

\begin{figure}[h]
    \centering
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/time-frequency-spectrum/P1-slow-down.png}
        \caption{Pump P1 turns off}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/time-frequency-spectrum/P2-speed-up.png}
        \caption{Pump P2 turn on}
    \end{subfigure}
\end{figure}

\subsection{Bearing defect frequencies}
% Domain expert analysis
% Bearing frequencies table
\begin{table}[h]
\centering
\begin{tabular}{|l|r|r|r|}
\hline
\textbf{Placement}     & \multicolumn{1}{l|}{\textbf{Motor \#1}} & \multicolumn{1}{l|}{\textbf{Motor \#2}} & \multicolumn{1}{l|}{\textbf{Pump \#3 \& \#4}} \\ \hline
\textbf{Bearing}       & \multicolumn{1}{l|}{6319-C3}            & \multicolumn{1}{l|}{6324-C3}            & \multicolumn{1}{l|}{6317-2Z}                  \\ \hline
\textbf{$n$}           & 8                                       & 8                                       & 8                                             \\ \hline
\textbf{$f_s$}         & 1493                                    & 1493                                    & 1493                                          \\ \hline
\textbf{$d$ {[}mm{]}}  & 33.12                                   & 41.28                                   & 30.00                                         \\ \hline
\textbf{$D$ {[}mm{]}}  & 147.5                                   & 190.0                                   & 132.5                                         \\ \hline
\textbf{$\beta$}       & 0                                       & 0                                       & 0                                             \\ \hline
\textbf{RPM {[}Hz{]}}  & 24.88                                   & 24.88                                   & 24.88                                         \\ \hline
\textbf{BPFO {[}Hz{]}} & 77.18                                   & 77.91                                   & 77.00                                         \\ \hline
\textbf{BPFI {[}Hz{]}} & 121.88                                  & 121.16                                  & 122.07                                        \\ \hline
\textbf{BSF {[}Hz{]}}  & 58.20                                   & 59.97                                   & 57.77                                         \\ \hline
\textbf{FTF {[}Hz{]}}  & 9.65                                    & 9.74                                    & 9.63                                          \\ \hline
\end{tabular}
\end{table}

% Bearing defect frequencies
\begin{figure}[h]
    \centering
    \begin{subfigure}[b]{0.24\textwidth}
        \includegraphics[width=\textwidth]{assets/results/defects/motors.png}
        \caption{Motors}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.24\textwidth}
        \includegraphics[width=\textwidth]{assets/results/defects/motors-dB.png}
        \caption{Pumps}
    \end{subfigure}
    \begin{subfigure}[b]{0.24\textwidth}
        \includegraphics[width=\textwidth]{assets/results/defects/pumps.png}
        \caption{Motors}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.24\textwidth}
        \includegraphics[width=\textwidth]{assets/results/defects/pumps-dB.png}
        \caption{Pumps dB}
    \end{subfigure}
\end{figure}

\subsection{Pump long-term monitoring}

% Total vibration levels - challange - long-live span (5 years)
\begin{figure}[h]
    \centering
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{assets/results/ksb-cloud/p1.png}
        \caption{Pump P1}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{assets/results/ksb-cloud/p2.png}
        \caption{Pump P2}
    \end{subfigure}
    \caption{Vibration levels}
\end{figure}

% Reverse engineer of spectra (low resolution)
\begin{figure}[h]
    \centering
    \includegraphics[width=0.8\textwidth]{assets/results/ksb-cloud/spectrum.png}
    \caption{Frequency spectrum}
\end{figure}

>>>>

\section{MaFaulDa in k-nearest neighbors}
The four outlined experiments on MaFaulDa involve testing sets of features with very few members to see the effects in predictions when reducing the information content about machine status to the minimum. First, the attributes are left in the complete count after extraction. Then, all of their combinations are enumerated, and the resulting accuracy distribution is matched against accuracy after feature selection with similarity metrics.

@@

Labeling every \nth{10} sample (10\% of the dataset) with a tumbling window of 10 samples reduces maximum accuracy for the three-predictor model compared to data points without gaps in labels. Time-domain features it is decreased by 9.9\% to 66.78\%, and by 14.93\% for frequency-domain features to 67.00\% (Fig.~\ref{fig:evaluation:label-skips-online}). More annotations can be scrapped in the case of a relabeled dataset where keeping just 0.02\% of the class labels produces a decrease by 13.7\% to 68.79\% for time domain attributes, and by 16.59\% to 66.25\% for frequency domain attributes.

\section{Industrial dataset analysis}
The latter part of the solution evaluation focuses on signal properties of vibrations from air compressors, water pumps, and electric induction motors. At first, the accelerometer data logger functionality is tested, and its precision is checked up in the known situations. Our custom dataset is compiled from collected measurements during regular operations of machines. The behaviour of different machines is compared using static frequency estimation and a time-frequency spectrogram. The methodology is carried out to diagnose the current status of water pumps. The presence of fault is confronted with sensor logs from the pump vendor.

\subsection{Data logger verification}
Data logger capabilities were verified by capturing vibrations on the back of the plastic casing for the electric motor of the standing fan. The recording is able to run continuously for more than one minute without dropping any samples. The amplitude range after conversion is constrained in the expected range (Fig.~\ref{fig:evaluation:logger-waveform}). The same amplitudes were obtained previously on a proof-of-concept device using analog accelerometer ADXL335 on Beaglebone Black, albeit with lower sensitivity.

\begin{figure}[h]
    \centering
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{assets/results/standing-fan/waveform.png}
        \caption{Time waveform}
        \label{fig:evaluation:logger-waveform}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{assets/results/standing-fan/standing-fan-accel.png}
        \caption{Estimation of rotation speed}
        \label{fig:evaluation:logger-fan-speed}
    \end{subfigure}
    \caption{Vibrations from the back of a standing fan in the radial direction}
\end{figure}

Time waveform captures mostly regular patterns of oscillatory motion  (Fig.~\ref{fig:evaluation:logger-waveform}). At slower speeds, the vibrations are higher because the fan is less stable and wobbles around the support. Timestamps from the sensor calibrate the sampling frequency from the theoretical 26667 Hz to the actual 26866 Hz. The estimate of fan rotational speed (Fig.~\ref{fig:evaluation:logger-fan-speed}) is accurate within the margin of error.

\subsection{Signal waveforms}
\begin{figure}[h]
    \centering
    \begin{subfigure}[b]{0.32\textwidth}
        \includegraphics[width=\textwidth]{assets/results/eda/frequency-spectrum-motors.png}
        \caption{Motors}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.32\textwidth}
        \includegraphics[width=\textwidth]{assets/results/eda/frequency-spectrum-pumps.png}
        \caption{Pumps}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.32\textwidth}
        \includegraphics[width=\textwidth]{assets/results/eda/frequency-spectrum-compressors.png}
        \caption{Compressors}
    \end{subfigure} 
    \caption{Wideband frequency waveform of machinery vibartions in Pump dataset}
    \label{fig:evaluation:wideband-frequencies}
\end{figure}

The overview of wideband vibration frequency spectra from various sensor placements shows clear distinctions among the machines. The recordings in Figure~\ref{fig:evaluation:wideband-frequencies} present consistent shapes of waveforms found during repeated trials. The spectra are Welch's average of 32768 long windows with 50\% overlap over minute of recording.

The electric motor signals are polluted by noise from the wind blowing out of a large cooling fan at the back of the motor. The M2 in place two compared to M1 has elevated amplitudes above 4 kHz. The pumps have richer signal content, likely due to the flow of water split into several frequency bands. The outer bearing (4) has a more attenuated amplitude above 1.5 kHz than the inner bearing (3). The P2 exhibits less vibration in comparable bands in general. The compressor casing produces a series of harmonics of rotational frequency, which are stronger near the scroll and suction valve than near the base.

\begin{table}[h]
\centering
\begin{tabular}{|l|r|r|r|}
\hline
\textbf{Placement}     & \multicolumn{1}{l|}{\textbf{M1}} & \multicolumn{1}{l|}{\textbf{M2}} & \multicolumn{1}{l|}{\textbf{P3, P4}} \\ \hline
\textbf{Bearing}       & \multicolumn{1}{l|}{6319-C3}            & \multicolumn{1}{l|}{6324-C3}            & \multicolumn{1}{l|}{6317-2Z}                  \\ \hline
\textbf{Rolling elements $n$}           & 8                                       & 8                                       & 8                                             \\ \hline
\textbf{Rotational speed $f_s$ {[}rpm{]}}         & 1493                                    & 1493                                    & 1493                                          \\ \hline
\textbf{Inner diameter $d$ {[}mm{]}}  & 33.12                                   & 41.28                                   & 30.00                                         \\ \hline
\textbf{Outer diameter$D$ {[}mm{]}}  & 147.5                                   & 190.0                                   & 132.5                                         \\ \hline
\textbf{Contact angle $\beta$}       & 0                                       & 0                                       & 0                                             \\ \hline
\textbf{RPM {[}Hz{]}}  & 24.88                                   & 24.88                                   & 24.88                                         \\ \hline
\textbf{BPFO {[}Hz{]}} & 77.18                                   & 77.91                                   & 77.00                                         \\ \hline
\textbf{BPFI {[}Hz{]}} & 121.88                                  & 121.16                                  & 122.07                                        \\ \hline
\textbf{BSF {[}Hz{]}}  & 58.20                                   & 59.97                                   & 57.77                                         \\ \hline
\textbf{FTF {[}Hz{]}}  & 9.65                                    & 9.74                                    & 9.63                                          \\ \hline
\end{tabular}
\caption{Bearing characteristic harmonic frequencies of pumps and their motors}
\label{tab:evaluation:bearing-freq-pump}
\end{table}

\begin{figure}[h]
    \centering
    \begin{subfigure}[b]{0.24\textwidth}
        \includegraphics[width=\textwidth]{assets/results/defects/motors.png}
        \caption{Motors}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.24\textwidth}
        \includegraphics[width=\textwidth]{assets/results/defects/motors-dB.png}
        \caption{Pumps}
    \end{subfigure}
    \begin{subfigure}[b]{0.24\textwidth}
        \includegraphics[width=\textwidth]{assets/results/defects/pumps.png}
        \caption{Motors}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.24\textwidth}
        \includegraphics[width=\textwidth]{assets/results/defects/pumps-dB.png}
        \caption{Pumps dB}
    \end{subfigure}
    \caption{Characteric bearing frequencies of pumps}
    \label{fig:evaluation:bearing-freq}
\end{figure}

Domain experts recommended the procedure for fault identification by calculation of bearing characteristic frequencies (Tab.~\ref{tab:evaluation:bearing-freq-pump}), and then they approved the following results. Figure~\ref{fig:evaluation:bearing-freq} identifies harmonics of rotational speed and BPFO frequency in every machine and BPFI for M2-2. It can be assumed that those frequencies will be the reason for their damage in the future. The absolute acceleration is minuscule in current frequency bands and year-long sensor log of rms velocity (Fig~\ref{fig:evaluation:ksb-guard-rms-vibartions}).

\begin{figure}[h]
    \centering
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{assets/results/ksb-cloud/p1.png}
        \caption{Pump P1}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{assets/results/ksb-cloud/p2.png}
        \caption{Pump P2}
    \end{subfigure}
    \caption{Vibration rms levels for a period over a year from KSB Guard}
    \label{fig:evaluation:ksb-guard-rms-vibartions}
\end{figure}

Therefore, the current results suggest that the bearings are in flawless condition. During the over five years the pump has been in service, there is not one instance of bearing fault due to rated lifespan and yearly prophylactic maintenance. This underscores the difficulty of the scarcity of non-faulty states in industrial environments. The monitoring is better suited for situations without preventive maintenance or with smaller machinery like the plunger pump BC~21/20S we considered during air conditioning inspections.

\begin{figure}[h]
    \centering
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/time-frequency-spectrum/K3-z-STFT-1kHz.png}
        \caption{C1}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/time-frequency-spectrum/M1-2-z-STFT-1kHz.png}
        \caption{M1-2}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/time-frequency-spectrum/P1-3-z-STFT-1kHz.png}
        \caption{P1-3}
    \end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/time-frequency-spectrum/P3-3-z-STFT-1kHz.png}
        \caption{P3-3}
    \end{subfigure}
    \caption{Machinery vibration spectrograms ($f_s$ = 26.8~kHz, $w$ = 8~kS)}
    \label{fig:evaluation:spectrograms}
\end{figure}

Spectrograms point out that under constant machine load, the significant frequencies stay more or less unchanged over time (Fig~\ref{fig:evaluation:spectrograms}). The resolution of the chart unit area is 306.95 ms and 3.26 Hz. Its magnitude is colored for decibel value.

\begin{figure}[h]
    \centering
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/time-frequency-spectrum/P1-slow-down.png}
        \caption{P1 turns off ($w$ = 4~kS)}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/time-frequency-spectrum/P2-speed-up.png}
        \caption{P2 turns on ($w$ = 32~kS)}
        \label{fig:evaluation-sigma-pump-interference}
    \end{subfigure}
    \caption{Vibrations of water pumps during switch over ($f_s$ = 26.8~kHz)}
    \label{fig:evaluation:pump-switch-over}
\end{figure}

The water pump switch on and off creates a fast change in shaft speed, which cannot be analyzed for resonance bands with enough time resolution by an automatic system at a chosen sampling rate. Due to inertia, slowing down takes about 10 seconds, whereas the speed up is half a second (Fig.~\ref{fig:evaluation:pump-switch-over}. The interference from excessive vibrations of the adjacent Sigma pump is picked up by the accelerometer on the KSB pump just before their switchover occurs (Fig~\ref{fig:evaluation-sigma-pump-interference}).

\begin{figure}[h]
    \centering
    \begin{subfigure}[b]{\textwidth}
        \includegraphics[width=\textwidth]{assets/results/feature-values/pumps-TD-dim-3.png}
        \caption{Time-domain features}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{\textwidth}
        \includegraphics[width=\textwidth]{assets/results/feature-values/pumps-FD-dim-3.png}
        \caption{Frequency-domain features}
    \end{subfigure}
    \caption{The atrribute value ranges of Pump dataset}
\end{figure}

The range of feature values for compressors and pumps are higher than in MaFaulDa despite most of them describing baseline status (Fig~\ref{fig:evaluation-sigma-pump-interference}). The increses can be seen for example on the interquartile range of rms (7.33 - 14.62 $\mathrm{m/s}^2$), centroid (3806 - 6003 Hz) or entropy (9.40 - 13.22 nats).

### 2024-05-07 thesis/chapters/06-conclusion.tex
Feature selection methods evaluated
Complete evaluation

Attributes extracted to describe machine behavior come mainly from descriptive statistics, audio signal processing studies, and vibrodiagnostics technical standards (ISO 20186 and ISO 13343). These formulas compute 10 features summarizing the waveform in the temporal domain and 11 features characterizing spectral density estimation in 3 spatial directions \textbf{(RQ1)}.

@@

Feature subsets are subjected after normalization to a k-nearest neighbor classifier that ascertains their relative fault detection power. Because of model overtraining with small k, the feature triplets equal or slightly outperformed the whole set of features on the validation set with accuracy up to 10\%. The spectral features reach higher accuracies than temporal because of their smaller interdependency \textbf{(RQ3)}.

The ensemble of feature selection with rank product produces the best model performance out of three combined in the majority of situations. No approach could find a triplet of predictors with an accuracy close to optimal one discovered exhaustively. Training on three principal components produced better accuracy than filtering feature selection, but PC mapping onto original trend indicators is unclear even in loading plots \textbf{(RQ3)}.

@@

Conclusions so far have been made on the MaFaulDa dataset imitating the realistic conditions. Therefore, in proper validation of the proposed solution in practice, we will compare it with the custom-made dataset.

@@

Feature selection methods should be incorporated into incremental learning. Hyperparameters shall be adjusted, and the balancing method used to increase model performance. The outlined tasks awaiting completion are planned for the DP~\rom{3} phase.

>>>>

Attributes extracted to describe machine behavior come mainly from descriptive statistics, audio signal processing studies, and vibrodiagnostics technical standards (ISO 20186 and ISO 13343). These formulas compute ten features summarizing the waveform in the temporal domain and eleven features characterizing spectral density estimation in axis of motion or all three spatial directions \textbf{(RQ1)}.

@@

Feature subsets are subjected after normalization to a k-nearest neighbor classifier that ascertains their relative fault detection power. Because of model overtraining with small k, the feature triplets equal or slightly outperformed the whole set of features on the validation set with accuracy up to 10\%. The time-domain set of features reach higher accuracies than frequency-domain set because of their smaller interdependency \textbf{(RQ3)}.

The ensemble of feature selection with rank product produces the best model performance out of three combined in the majority of situations. No approach could find a triplet of predictors with an accuracy close to optimal one discovered exhaustively. 
%TODO wtf
Training on three principal components produced better accuracy than filtering feature selection, but PC mapping onto original trend indicators is unclear even in loading plots \textbf{(RQ3)}.

@@

@@

%TODO
% Future work
% - long term dataset from machinery until failure or propose way for factories to artifically train model for new machinery - make the system machine and placement independent
% - more diffenent feature set from one recoding - in windows
% - combine feature selection with incremntal learining
% - Different election methods and metrics
% - Find other ML model also suitable HoeffdingTreeClassifier - losing original data for labeling - mechnaism of transforming samples to model represntatin
% - Monitor more machines and combine their result with federated learning
% - Monitor faults of different equipment - moving wheels of the train or train tracks

% Main points of the thesis assigments namely effectivness representation of machinery faults in succint fashion and performance in machine learining diagnostics models has been compared extensively.

### 2024-05-07 thesis/chapters/preliminaries/acknowledgments.tex
Complete evaluation

\vspace*{\fill}
\section*{Poďakovanie}
{\linespread{1.0}\small Napriek tomu, že tento text je len kvapka v mori záverečných prác, pre mňa bol proces tvorby omnoho viac než zachytávajú slová na stránkach. Srdečná vďaka patrí školiteľovi Ing.~Marcelovi Balážovi,~PhD. a konzultantovi Ing.~Lukášovi Doubravskému z firmy R-DAS,~s.r.o. Obaja boli otvorení mojim všemožným nápadom a podporovali ma v ich realizácii aj cez mnohé ťažkosti. Za praktický expertný pohľad na vibrodiagnostiku vďačím prof. Ing.~Stanislavovi Žiaranovi,~CSc. a Ing.~Ondrejovi Chlebovi,~PhD. zo Strojníckej fakulty STU. Cením si ústretovosť Bratislavskej vodárenskej spoločnosti,~a.s., konkrétne Ing.~Petrovi Kmeťkovi a Ing.~Peterovi Csókovi, v sprístupnení čerpadiel na merania a súvisiacich podkladov. Rovnako ďakujem za ochotu firme VNET,~a.s., a síce Michalovi Országovi a Mgr.~Vladimírovi Kupčovi za odporúčania možných strojov na merania v dátových centrách a sprístupnenie kompresorov. Prácu by som rád venoval rodine a kolegom-kamarátom, ktorí stáli pri mne na ,,šialenej akademickej dráhe'' a podnetné diskusie s nimi prispeli aj k môjmu pohľadu na odborné problémy. Nuž a v konečnom dôsledku som mal niekedy len viac šťastia ako rozumu.}
\vspace{3cm}

>>>>

\vspace*{\fill}
\section*{Poďakovanie}
{\linespread{1.0}\small Napriek tomu, že tento text je len kvapka v mori záverečných prác, pre mňa bol proces tvorby omnoho viac než zachytávajú slová na stránkach. Srdečná vďaka patrí školiteľovi Ing.~Marcelovi Balážovi,~PhD. a konzultantovi Ing.~Lukášovi Doubravskému z firmy R-DAS,~s.r.o. Obaja boli otvorení mojim všemožným nápadom a neochvejne ma podporovali v ich realizácii aj cez mnohé ťažkosti. Za praktický expertný pohľad na vibrodiagnostiku vďačím prof. Ing.~Stanislavovi Žiaranovi,~CSc. a Ing.~Ondrejovi Chlebovi,~PhD. zo Strojníckej fakulty STU. Cením si ústretovosť Bratislavskej vodárenskej spoločnosti,~a.s., konkrétne Ing.~Petra Kmeťka a Ing.~Petera Csóku, v sprístupnení čerpadiel na merania a súvisiacich podkladov. Rovnako ďakujem za ochotu firme VNET,~a.s., a síce Michalovi Országovi a Mgr.~Vladimírovi Kupčovi za odporúčania možných prvkov na merania v klimatizáciach pre dátové centrá a sprístupnenie kompresorov. Prácu by som rád venoval rodine a kolegom-kamarátom, ktorí stáli pri mne na ,,šialenej akademickej dráhe'' a podnetné diskusie s nimi prispeli aj k môjmu pohľadu na odborné problémy. Nuž a v konečnom dôsledku som mal niekedy len viac šťastia ako rozumu.}
\vspace{3cm}
